Exploring dimensions of biodiversity in Japanese ferns

### 2021-05-19 ms/manuscript.Rmd
Update MS

Characterizing the spatial distribution of biodiversity is a major goal of evolutionary biology with two equally important aspects: to understand the processes generating it, and to conserve it. The vast majority of studies seeking to understand the spatial distribution of biodiversity focus on species richness. Hotspots, or areas of exceptionally high richness, have received particular attention, resulting in a widely-recognized set of 34 terrestrial hotspots and motivating conservation strategies to preserve them. However, richness alone cannot provide a complete picture of biodiversity. All organisms are related by descent from a common ancestor, and these evolutionary relationships must be taken into account to obtain a full understanding of biodiversity.

@@

However, a comprehensive understanding of the relationships between richness and other metrics requires densely sampled data or can be lead astray.

The ferns of Japan are excellent model system because they have been the target of intense botanical interest for several decades and are densely sampled. One particularly valuable characteristic of this flora is the availability of data on reproductive mode (known for 221/721 taxa [70%]), which is likely to affect genetic diversity [@Bengtsson2003], and thereby higher-level biodiversity [@Krueger-Hadfield2019].

>>>>

Characterizing the spatial distribution of biodiversity is a major goal of evolutionary biology with two equally important aspects: to understand the processes generating it, and to conserve it. The vast majority of studies seeking to understand the spatial distribution of biodiversity focus on species richness. Hotspots, or areas of exceptionally high richness, have received particular attention, resulting in a widely-recognized set of 34 terrestrial hotspots [@Myers2000] and motivating conservation strategies to preserve them [@Margules2000; @Brooks2006]. However, richness alone cannot provide a complete picture of biodiversity. All organisms are related by descent from a common ancestor, and these evolutionary relationships must be taken into account to obtain a full understanding of biodiversity.

@@

However, a comprehensive understanding of the relationships between richness and other metrics requires densely sampled data, and such datasets are rare on the regional (country) scale. The ferns of Japan are excellent model system because they have been the target of intense botanical interest for several decades and are densely sampled. One particularly valuable characteristic of this flora is the availability of data on reproductive mode (known for 221/721 taxa [70%]), which is likely to affect genetic diversity [@Bengtsson2003], and thereby higher-level biodiversity [@Krueger-Hadfield2019].
